### Exercise 8 ###

(a) Use the read.csv() function to read the data into R. Call the loaded data college.

```{r}
college <- read.csv("College.csv")
```

(b) Look at the data using the fix() function. Convert first column of university name to row name and remove it from the data set.

```{r}
rownames(college) <- college[,1]

college <- college[,-1]
```

(c)

i. Use the summary() function to produce a numerical summary of the variables in the data set

```{r}
summary(college)
```

ii. Use the pairs() function to produce a scatterplot matrix of the first ten columns or variables of the data.

```{r}
pairs(college[,1:10])
```

iii. Use the plot() function to produce side-by-side boxplots of Outstate versus Private.

```{r}
college$Private <- as.factor(college$Private)
plot(x = college$Private, y = college$Outstate)
```

iv. Create a new qualitative variable, called Elite, by binning the Top10Perc variable.

```{r}
Elite <- rep("No",nrow(college))
Elite[college$Top10perc > 50] <- "Yes"
Elite <- as.factor(Elite)
college <- data.frame(college, Elite)
```

```{r}
summary(college)
```

```{r}
plot(x = college$Elite, y = college$Outstate)
```

v. Use the hist() function to produce some histograms with differing numbers of bins for a few of the quantitative variables. par(mfrow=c(2,2)) is useful to simutaneously plot several histograms

```{r}
par(mfrow=c(2,2))
hist(college$Outstate,breaks = 20)
hist(college$Books,breaks = 20)
hist(college$Personal,breaks = 20)
hist(college$Grad.Rate,breaks = 20)
```

### Exercise 9 ###

(a) Which of the predictors are quantitative, and which are qualitative?

```{r}
auto <- read.csv("Auto.csv")
auto$origin <- as.factor(auto$origin)
auto$horsepower <- as.numeric(auto$horsepower)
summary(auto)
```

(b) What is the range of each quantitative predictor?

```{r}
sapply(auto[, 1:7], range)
```

(c) What is the mean and standard deviation of each quantitative predictor

```{r}
sapply(auto[, 1:7], mean)
sapply(auto[, 1:7], sd)
```

(d) Now remove the 10th through 85th observations, what is the range, mean, and standard deviation of each predictor in the subset of the data that remains?

```{r}
sapply(auto[-c(10:85),1:7],range)
sapply(auto[-c(10:85),1:7],mean)
sapply(auto[-c(10:85),1:7],sd)
```

(e) Using the full data set, investigate the predictrs graphically, create some plots highlighting the relationships among the predictors.
(f) Suppose that we wish to predict gas mimleage on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting mpg?

```{r}
plot(auto$displacement, auto$mpg)
plot(auto$weight, auto$mpg)
plot(auto$year, auto$mpg)
plot(auto$origin, auto$mpg)
```

mpg is negatively correlated with displacement and weight. It is positively correlated with years and origin.

### Exercise 10 ###

(a) To begin, load in the Boston data set. The Boston data set is part of the MASS library in R.

```{r}
library(MASS)
Boston
```

(b) Make some pairwise scatterplots of the predictors (columns) in this data set. Describe your findings.

```{r}
pairs(Boston[,1:10])
```

(c) Are any of the predictors associated with per capita crime rate? If so explain the relationship.

```{r}
plot(Boston$dis, Boston$crim)
```

Distance seems to be a huge correlation factor. the closer it is to one of the five Boston employment centres, the higher the crime rate.

(d) Does any of the suburbs of Boston appear to have particularly high crime rates? Tax rates? Pupil-teacher ratios?

```{r}
par(mfrow=c(1,3))
hist(Boston$crim, breaks = 25)
hist(Boston$tax, breaks = 25)
hist(Boston$ptratio, breaks = 25)
```

(e) How many of the suburbs in this data set bound the Charles river

```{r}
dim(subset(Boston, chas == 1))
```

(f) What is the median pupil-teacher ratio among the tows in this data set?

```{r}
median(Boston$ptratio)
```

(g) Which suburb of Boston has lowest median value of owner-occupied homes?

```{r}
t(subset(Boston, medv == min(Boston$medv)))
```

(h) In this data set, how many of the suburbs average more than seven rooms per dwelling? More than eight rooms per dwelling?

```{r}
dim(subset(Boston, rm > 7))
```

```{r}
subset(Boston, rm > 8)
```

